---
title: "Online learning"
author: "Janno Vergara"
format:
    html:
        code-overflow: wrap
---

# AI for brainstorming and planning

Before using AI, define the problem that you are trying to solve, and why.

When using AI, provide necessary background information and context.

AI isn't perfect, so be a tough critic.

**Goals:**

- break through creative blocks
- find unexpected solutions to complicated problems
- turn your best ideas into action plans

Gain

- faster validation
- informed decisions
- industry awareness

## Brainstorm ideas with Gemini
### Build with AI: Strategic plan

Step 1: Brainstorm new product ideas

```{r}
#| output: false
"You are a [persona, e.g. marketing expert] in the [industry, e.g. audio industry]. My company is developing a [new product, e.g. new line of premium headphones]. Help me brainstorm [items to brainstorm, e.g. accessories or add-ons] that I could [purpose, e.g. bundle with this product]."
```

Step 2: Create a cost-benefit analysis table

```{r}
#| output: false
"Perform a [type of analysis, e.g. cost-benefit analysis] for each of these ideas. Format your response as a table with the following columns:

- [Column 1 name, e.g. Idea]

- [Column 2 name, e.g. Cost (low/medium/high)]

- [Column 3 name, e.g. Benefit (low/medium/high)]"
```

Step 3: Research industry trends

```{r}
#| output: false
"What are some current industry trends around [your product or industry]? I'd like to factor those insights into my decision."
```

Step 4: Schedule a recurring analysis

```{r}
#| output: false
"Run this analysis [desired frequency, e.g. once a week] so I can stay up to date on these trends."
```

Feedback. Why is this a bad idea.

## Create a project timeline with Gemini
### Build with AI: Risk assessment

Step 1: Identify missing project dependencies

```{r}
#| output: false
"You are a [persona, e.g. project manager]. My company is launching a [product, service or initiative]. I've attached [document 1, e.g. a launch memo] and [document 2, e.g. a launch work-back schedule]. Are there any dependencies missing from the plan?"
```

Step 2: Assess the risk of missing dependencies

```{r}
#| output: false
"Let's focus on [a missing dependency from Gemini’s previous response]. How do they affect the [overall project goal, e.g. the launch]?"
```

Step 3: Generate an updated project timeline

```{r}
#| output: false
"Create a timeline listing key milestones for [the missing dependency from the previous step]. Flag what might be missing from my current plan."
```

GO-to AI tool: NotebookLM

## Build a knowledge hub in NotebookLM

What you'll gain:

- Instant, accurate answers
- Reduced interruptions
- A source of truth

Step 1: Ask questions about your project documents

```{r}
#| output: false
"When are we starting [key phase in your project, e.g., full-scale packaging production]?"
```

Step 2: Share your notebook with your team
