---
title: "Online learning"
author: "Janno Vergara"
format:
    html:
        code-overflow: wrap
---

# Coursera - Google AI Fundamentals

## AI for data analysis

Elements of data analysis where role is essential:

- ask questions
- understand implications
- make decisions
- verify findings

Identify key metrics to inform your reporting

What you'll gain:

- Strategic focus
- Greater confidence
- Tool guidance

### Build with AI: Measurement plan

Step 1: Identify key presentation metrics

```{r}
#| output: false

"I work at an [your company type, e.g. apparel company].

I'm preparing for an [type of meeting, e.g. executive review of website performance].

Our goal is to [primary business goal, e.g. increase revenue in Q3].

What are the top 5 metrics I should consider for my presentation?"
```

Review Gemini's suggestions. You will use one of these metrics for the next step.

Step 2: Anticipate leadership questions

In the same chat with Gemini, paste the prompt below and replace the text in [brackets] with your own details.

```{r}
#| output: false
"What questions might our leadership team ask about [one of Gemini's suggested metrics from the previous step]?"
```

Read the potential questions Gemini suggests. As a next step, you can ask Gemini for guidance on how to find the data for your chosen metric.

Optional: Get data from a specific data source
If you know where to get your data but aren’t sure how to download it, you can prompt Gemini for help. Paste the prompt below and replace the text in [brackets] with your own details.

```{r}
#| output: false
"How do I export [data, e.g. website traffic data] from [data source, e.g. Google Analytics] so I can analyze it in [destination, e.g. a Google Sheet]?"
```

## Clean up messy data to conduct analysis

What you'll gain:

- New insights
- Easier analysis
- More time for strategy

### Build with AI: Clean data set

Step 1: Extract and format data from an image

Click the “New chat” button to start a new chat with Gemini. Then, upload a source file. If you don’t have your own, you can use this sample screenshot. Then, paste the prompt below and replace the text in [brackets] with your own details.

```{r}
#| output: false
"Extract the [data you want, e.g. reviews] from this [source, e.g. screenshot] and turn them into a [data format, e.g. table] with the following columns [column headers, e.g. date, text, and # of stars]."
```

Gemini will generate a table. Select "Export to Sheets" and open the new file indicated on the bottom-left of your window to continue.

Step 2: Annotate your data

In Google Sheets, create a new column. Give it a descriptive name (e.g. “customer sentiment”). In the first data cell of that new column, enter the formula below. Replace the text in [brackets] with your own details, ensuring you reference the cell containing the review text (e.g. B2).

```{r}
#| output: false
'=AI("Analyze the [data to classify, e.g. customer feedback] and classify it into [category list, e.g. Positive, Neutral, or Negative]", [cell with customer feedback text, e.g. B2])"'
```

## Analyze spreadsheet data using everyday language

What you'll gain:

- Insights without formulas
- Clear communication
- Faster decision making

Step 1: Get a high-level data summary
Import your data into a new Google Sheet. If you don’t have your own, you can use this  sample CSV. To open Gemini in Google Sheets, click the Gemini icon in the top-right corner. In the Gemini sidebar, paste the prompt below and replace the text in [brackets] with your own details.

```{r}
#| output: false
"This is data from [source of your data, e.g. my e-commerce website]. Provide the [first metric you want, e.g. total purchase revenue] and [second metric you want, e.g. total number of transactions].'
```

Review Gemini's summary. You can click "Analysis steps" to see the code Gemini generated.

Step 2: Ask a question about your data
In the same Google Sheet and Gemini sidebar, ask a question relevant to your dataset. For example:

```{r}
#| output: false
"What is the average revenue per session based on channel, regardless of device category?"
```

Review the output. You will use this insight in the next step.

Step 3: Use your data to build a narrative
Open a new tab and navigate to the Gemini app by entering the URL 
gemini.google.com. Paste the prompt below and replace the text in [brackets] with your own details to understand the "why" behind your data.

```{r}
#| output: false
"You are an [persona, e.g. data analyst]. For an [your business type, e.g. e-commerce site], why might the [specific finding from Step 2]?"
```

Read Gemini's explanation. You will use this narrative to complement your data visualization.

Step 4: Create a data visualization
Switch back to the Google Sheets tab. In the Gemini sidebar, paste the prompt below and replace the text in [brackets] with your own details.

```{r}
#| output: false
"Create a [chart type, e.g. bar chart] that shows [metric to visualize, e.g. average revenue per session] by [data column for chart axis, e.g. channel]."
```

Gemini will generate the chart and add it to your sheet. You can now use this visualization, along with the insights from the previous steps, in your reports or presentations.

## Build a business performance simulator for faster, data-driven decisions

- What you'll gain
- Adaptable Planning
- Strategic Alignment

Step 1: Identify your business levers  

Click the New chat button to start a new chat with Gemini. Then, paste the prompt below and replace the text in [brackets] with your own details. You can use this sample data or your own.

```{r}
#| output: false
"I’m a [your role] at [place of work e.g. an e-commerce business selling trousers]. My main goal is to [goal, e.g. increase my profit this year]. Acting as a business advisor, analyze my [type of data you upload to Gemini] and give me a list of the 3 most important changes I can make that would have the biggest impact on my goal."
```

Review the suggestions for potential changes that Gemini provides. You can ask Gemini to give you more options or iterate on them as well. You’ll use these potential changes to create the interactive simulator in the next step.

Step 2: Build an interactive simulator

Now, you’ll create an interactive simulator that lets you visualize the potential effect of the changes that Gemini suggested. In the same chat, select “Canvas” from the tools menu and paste the prompt below:

```{r}
#| output: false
"Based on those insights and my data, create an interactive [type of tool, e.g. profit calculator] for my [type of business]. Let me adjust [type of component e.g. toggles, sliders, switches] for each change to show their effect."
```

Adjust the variables and design of the tool to fit your needs. For example, you can adjust your average order value, current production spend, or monthly rent.

Step 3: Customize the design 

Change the design to fit your needs. For example, you could ask Gemini to adjust the visual design to match your company’s brand.

```{r}
#| output: false
"Can you give this [type of tool, e.g. profit calculator] more of a [type of design, color or theme]?"
```

Step 4: Use the calculator

Try using your new tool to explore your idea. For example: move your sliders to reflect a 15% increase in your first variable. Use the calculator to help you find how much you would need to change your other sliders to keep your profit from dropping below a certain level. 