---
title: "Online learning"
author: "Janno Vergara"
format:
    html:
        code-overflow: wrap
---

# Coursera - Google AI Fundamentals

- Turn complexity into clarity
- Tackle tough ambiguous problems
- Have support when making decisions

## Keep your teams on track with Gemini

When using AI for communication, your role is to apply strategic thinking and emotional intelligence to te table

- purpose and intent
- understanding the audience
- authenticity and voice
- accountability
- strategic judgment

Use AI as a thought partner to help you build your communication strategy

1. brainstorming
2. rapid drafting and variation
3. refining and polish
4. practice and simulation

Use AI to speed up the editing process to help bring your voice to life

### Automate notetaking

What you'll gain: 

- Focused meetings
- Actionable next steps
- Better team alignment

### Build with AI: Meeting summary

Step 1: Generate an action item report from a transcript. 

```{r}
#| output: false
"Acting as [a role that would excel at the task you want to accomplish, e.g. a senior project manager], generate a report based on the attached transcript.

The report must have the following sections: [description of the sections you want in the report].
"
```

Step 2: Evaluate the report

```{r}
#| output: false
"Evaluate the report using these criteria:

- [First criteria, e.g. Brevity]

- [Second criteria, e.g. Clear action items]

- [Third criteria, e.g. Clarity]
"
```

## Pressure-test ideas in Gemini

### Get feedback to strengthen your work

What you'll gain:

- Increased confidence
- Stronger proposals
- Diverse viewpoints

Step 1: Give Gemini a persona to get feedback 

```{r}
#| output: false
"I’m working on a [type of document, e.g. proposal or report] for [brief description of your project].

Act as the [stakeholder you want feedback from and list their priorities], and review the document attached.

From your perspective, is there any information missing?"
```

Step 2: Work through potential edits

```{r}
#| output: false
"You provided the following feedback about [feedback topic, e.g. the proposal is not detailed enough].

I plan to resolve your feedback by [proposed resolution, e.g. including a timeline, budget, and resourcing].

Does that resolve the concerns, or are you looking for more?"
```

Step 3: Draft a summary based on your new details

```{r}
#| output: false
"How would you write a [desired length, e.g. 2-sentence] summary of this plan for the [document, e.g. one-pager]?"
```

## Draft communications with Gemini Canvas

What you'll gain: 

- Stakeholder alignment
- Communication efficiency
- Interactive refinement

### Build with AI: Communications kit

Step 1: Extract key points from a source document

```{r}
#| output: false
"I’m a [your role, e.g. project manager] responsible for [the project, e.g. the launch] described in the document attached.

I’m working on [a piece of communication, e.g. an email] announcing [the topic, e.g. the launch] to [the audience, e.g. the full company].

Pull [number] key points from the document that I can use in my message."
```

Step 2: Identify stakeholder-specific points

```{r}
#| output: false
"Select some points specifically for two key stakeholders: [stakeholder 1, e.g. our CFO] and [stakeholder 2, e.g. our operations manager].

Start by thinking about their priorities based on their roles before choosing the points I should highlight for each."
```

Step 3: Draft a stakeholder email in Canvas

```{r}
#| output: false
"Draft the email to [stakeholder 1].

Include the [Gemini's prioritized points from the previous step] as [format, e.g. bullets]."
```

Step 4: Refine the draft using inline edits

```{r}
#| output: false
"Make this [desired change, e.g. shorter or more formal]."
```

What's the difference between using the Gemini app and using Canvas?

In canvas, you can just highlight certain portions of the text and have a conversation with Gemini about that.

## Get speech feedback from Gemini Live

What are you most excited about for the future of AI?

Everything will have a conversational interface.

### Practice talking points to build confidence

What you'll gain:

- On-demand practice
- Greater preparedness
- Actionable feedback

### Build with AI: Sales pitch